Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-07-04 tex/figures.tex
prettify noise_realization figure, some minor changes in discussion text
prettier plots, add soem info in text about GP not having same degeneracies with real parameters as a polynomial

\begin{figure}[h!]
\begin{center}
\includegraphics[width = 0.5 \textwidth]{figures/data.pdf}
\caption{Observational data. 
Top: The calibrated spectrum for \excluster.
Middle: The signal-to-noise ratio.
Bottom: The spectrophotometric calibration vector determined by
\citet{schiavon05}. Note the wiggles in the calibration vector\label{fig:ggc_data}}
\end{center}
\end{figure}

@@

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset of the posteriors from the input parameters for
inference from mock spectra and photometry, as a function of the mock
parameter that is varied.  The medians of the posterior PDFs are shown
as connected black circles, the 16th and 84th percentile of the
posteriors are indicated by the gray shaded region.
Left: Results when varying age.
Middle: Results when varying metallicity.
Right: Results when varying dust attenuation.
 \label{fig:mock_parameter_space}}
\end{figure*}

>>>>

%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width = 0.5 \textwidth]{figures/data.pdf}
%\caption{Observational data. 
%Top: The calibrated spectrum for \excluster.
%Middle: The signal-to-noise ratio.
%Bottom: The spectrophotometric calibration vector determined by
%\citet{schiavon05}. Note the wiggles in the calibration vector\label{fig:ggc_data}}
%\end{center}
%\end{figure}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/components.pdf}
\caption{Components of the spectroscopic calibration.  
Top Left: Posterior samples of the smooth component of the calibration
vector, the exponential of a polynomial.  The input true calibration
vector is shown in {\it black}.
Bottom Left: The Gaussian Process prediction conditioned on the residual
between the data and posterior samples of the mean model including the
smooth calibration component.
Top Right: Posterior samples of the sum of the smooth calibration
component and the Gaussian Process prediction, compared to the input
true calibration vector ({\it black}).
Bottom Right: Ratio of the sum of the smooth calibration component and
the Gaussian Process prediction to the input
calibration vector ({\it black}).
\label{fig:components}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset of the posteriors from the input parameters for
inference from mock spectra and photometry, as a function of the mock
parameter that is varied.  The medians of the posterior PDFs are shown
as connected black circles, the 16th and 84th percentile of the
posteriors are indicated by the gray shaded region.
Left: Results when varying age.
Middle: Results when varying dust attenuation.
Right: Results when varying metallicity.
 \label{fig:mock_parameter_space}}
\end{figure*}

### 2015-07-04 tex/ms.tex
prettier plots, add soem info in text about GP not having same degeneracies with real parameters as a polynomial

{\color{blue} BDJ This paragraph should explain why we are using the
GP, not just how it works.}
For the spectroscopic measurements we are going to account for the
spectrophotometric calibration in our likelihood function.  We take
this calibration-vector that modifies the mean spectroscopic model to
produce the observed spectrum to be multiplicative with respect to the
mean model.  The multiplicative calibration vector can be explicitly
modeled, for example using polynomials.  However, for complex
calibration vectors over large wavelength ranges, the number of
parameters required to model the calibration can become quite large
(e.g. very high order polynomials) and the correct parameterization
may be unknown.  It is therefore desirable to introduce a
non-parameteric model of the calibration.  We do this using a Gaussian
Process: BDJ: prior over functions, analytically marginalizable,
covariant fractional uncertainties the same as multiplying by a
function (covariant uncertainties the same as adding a function.)

@@

\item \sout{Mock perfectly calibrated data: inference using spectroscopy and one
  photometric band, with the full calibration model.  This is how much
  including additional calibration flexibility hurts the posterior
  PDFs compared to perfectly known calibration.}

\item \sout{Mock uncalibrated data:  inference using spectroscopy and one
  photometric band, with full calibration model.  This is how well we
  can get the calibration \emph{and} the physical parameters with
  spectroscopy only.}

@@

\item Real uncalibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model.

@@

\item how (some) of these things vary with S/N

>>>>

{\color{blue} BDJ This paragraph should explain why we are using the
GP, not just how it works.}
For the spectroscopic measurements we are going to account for the
spectrophotometric calibration in our likelihood function.  We take
this calibration-vector that modifies the mean spectroscopic model to
produce the observed spectrum to be multiplicative with respect to the
mean model.  The multiplicative calibration vector can be explicitly
modeled, for example using polynomials.  However, for complex
calibration vectors over large wavelength ranges, the number of
parameters required to model the calibration can become quite large
(e.g. very high order polynomials) and the correct parameterization
may be unknown.  It is therefore desirable to introduce a
non-parameteric model of the calibration.  We do this using a Gaussian
Process: BDJ: prior over functions, analytically marginalizable,
covariant fractional uncertainties the same as multiplying by a
function (covariant uncertainties the same as adding a function.)
Using a polynomial can result in degeneracies between model and
polynomial parameters, whereas GP is only for things that {\it can't}
be fit by model.

@@

\item \sout{Mock perfectly calibrated data: inference using
spectroscopy and one photometric band, with the full calibration
model.  This is how much including additional calibration flexibility
hurts the posterior PDFs compared to perfectly known calibration.}
Make sure this is run for the linear model, make sure it is converged.

\item \sout{Mock uncalibrated data:  inference using spectroscopy and one
  photometric band, with full calibration model.  This is how well we
  can get the calibration \emph{and} the physical parameters with
  spectroscopy only.}
Make sure this is run for the linear model.

@@

\item \sout{Real uncalibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model. } Make sure this is
converged, make sure priors and jitter make sense.

@@

\item how parameter inference varies with photometric S/N.  Do for mag
  uncertainties of 0.05.
